Data Formatting

### 2021-03-29 scripts/data_format.Rmd
clean up packages
make updates for supp fig 3 and 4

Packages
```{r}
library(tidyverse)
library(magrittr)
library(vegan)
library(here)
```

@@

>>>>

Packages
```{r}
library(tidyverse)
library(magrittr)
library(vegan)
library(patchwork)
library(ggnewscale)
library(here)
```

@@

Make matrix for environmental variables
```{r}
#select for environmental variables
env <- data %>% dplyr::select(WetAltID, Month.1, MeanAirT, MeanWaterTempPredC, DryingScore, CanopyCover, Area, Perimeter) %>% distinct() %>% arrange(.,WetAltID) 
env$Month.1 <- gsub("Month", "", env$Month.1)
#make siteID rowname
env$siteID <- paste(env$WetAltID, env$Month.1, sep = "_")
env %<>% dplyr::select(-WetAltID, -Month.1)
#remove duplicated rows (siteID is duplicated but env. variables are not... not sure why this is)
env <- env[-c(53, 90),]
env_mat <- env %>% column_to_rownames(., var = "siteID")
```
